### 2019-04-15 paper/paper.tex
literally only need one graph and three tables

\subsection{Relationships between Measures}
[NEEDS MORE DATA]

\subsection{Distinct Package Types}
[NEEDS MORE DATA]

>>>>

\subsection{Relationships between Measures}\label{metricDiff}

In order to evaluate how different popularity metrics
relate to each other and for what purposes they can be used,
we investigate the relationships between our three chosen metrics.
By calculating the Spearman rank correlation coefficients between
the metrics, we are able to support the findings of the original 
paper for the subset of packages for which this correlation is applicable,
i.e., only those packages which have assigned ranks for each measure used
in calculating the correlation coefficient. The coefficients presented 
in Table \ref{corr} are similar to those found in the original paper, 
supporting the idea that each measure of popularity does not always
represent the same kind of intrinsic properties of a package, and
thus cannot necessarily be used interchangeably.

To inspect these relationships in greater detail, Figure \ref{corrGraph}
plots the differences between ranks of each metric. It may be observed
that our data presents a relatively normal distribution of differences
between popularity ranks, again matching the findings of the original paper \cite{Wittern:2016}.
From these results, we can conclude that our three metrics of popularity
are measures of different package attributes, and that packages
with a high rank in one metric can be ranked much lower by another metric.

\subsection{Distinct Package Types}

As we demonstrated in section \ref{metricDiff}, packages that perform well
by one measure of popularity often perform poorly by others. The original paper
proposes that one major source of this differential is in the way that packages
are used \cite{Wittern:2016}. It is surmised that packages ranked highly by the
\code{npm} PageRank system are primarily packages that are used often within the
\code{npm} ecosystem, and tend to be \textbf{core utility} packages that are used
as dependencies for other \code{npm} packages, and rarely used outside of the
\code{npm} package environment. Conversely, packages that exhibit
significant popularity by the \code{GitHub} rank tend to be \textbf{end user} packages more
commonly used in application development as opposed to package construction. 
In order to confirm this hypothesis, we examine keywords associated with each
ranking system, as is done in the original paper.
Tables \ref{npmStrong} and \ref{githubStrong} display keywords most associated with
each popularity ranking. As the keywords in Table \ref{npmStrong} are closely linked to 
low level utilities, and the keywords of Table \ref{githubStrong} are strongly related to
application frameworks, we feel confident confirming the hypothesis of the original authors.
